CDC data Exercise

### 2024-07-10 cdcdata-exercise/cdcdata-exercise.qmd
page for CDCdata cleaning exercise
Updating CDC data wrong label found

---
title: "loading/cleaning/wrangling/exploring"
author: "Edward Cruz"
format: docx
---

@@

# Bar chart of Death Count by State with skyblue fill and flipped coordinates
ggplot(data = DthCount3A_cleaned, aes(x = State, y = Death_Count)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  labs(title = "Varroa Mites by State",
       x = "State",
       y = "Death Count") +
  theme_minimal() +
  coord_flip() +
  theme(
    axis.text.x = element_text(size = 12),  # Adjust the size as needed
    plot.title = element_text(hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text.y = element_text(size = 10)
  )

@@

# Bar chart of Death Count by State with skyblue fill and flipped coordinates
ggplot(data = DeathCntFinal_data, aes(x = State, y = Death_Count)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  labs(title = "Varroa Mites by State",
       x = "State",
       y = "Death Count") +
  theme_minimal() +
  coord_flip() +
  theme(
    axis.text.x = element_text(size = 12),  # Adjust the size as needed
    plot.title = element_text(hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text.y = element_text(size = 10)
  )

>>>>

---
title: "CDC data Exercise"
---

Placeholder file for cdc data coding exercise.

## Loading and Checking Data
### Import libraries

@@

# Bar chart of Death Count by State with darkblue fill and flipped coordinates
ggplot(data = DthCount3A_cleaned, aes(x = State, y = Death_Count)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  labs(title = "Death Count by State",
       x = "State",
       y = "Death Count") +
  theme_minimal() +
  coord_flip() +
  theme(
    axis.text.x = element_text(size = 12),  # Adjust the size as needed
    plot.title = element_text(hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text.y = element_text(size = 10)
  )

@@

# Bar chart of Death Count by State with skyblue fill and flipped coordinates
ggplot(data = DeathCntFinal_data, aes(x = State, y = Death_Count)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  labs(title = "Death Count by State",
       x = "State",
       y = "Death Count") +
  theme_minimal() +
  coord_flip() +
  theme(
    axis.text.x = element_text(size = 12),  # Adjust the size as needed
    plot.title = element_text(hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text.y = element_text(size = 10)
  )
